### 2024-03-28 paper/paper.qmd
update

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(arrow)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-28 scripts/00-simulate_data.R

@@ -1,19 +1,41 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates a relationship between the beauty and employment that how will be impact on the hiring process in US.
+# Author: Sky Suh
+# Date: 28 March 2024
+# Contact: sky.suh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# Any other information needed? 
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+simulated_data <-
+  tibble(
+    certainty = runif(n = 1000, min = 0, max = 11) |> floor (),
+    guessed_correct = runif(n = 1000, min = 0, max = 11) |> floor (),
+  )
 
+### Add tests for simulated data ###
+# Expect that guessed_correct is only ever 0 or 1.
+max(simulated_data$certainity) == 1
+min(simulated_data$certainity) == 0
+any(unique(simulated_data$certainity) == c(0:1)
 
+# Expect that certainty is only ever an integer 0 to 10, inclusive.
+max(simulated_data$certainity) == 10
+min(simulated_data$certainity) == 0
+any(unique(simulated_data$certainity) == c(0:18)
+    
+    #### Download data ####
+    # [...ADD CODE HERE TO DOWNLOAD...]
+    
+    
+    
+    #### Save data ####
+    # [...UPDATE THIS...]
+    # change the_raw_data to whatever name you assigned when you downloaded it.
+    write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 

### 2024-03-28 scripts/02-data_cleaning.R

@@ -1,14 +1,15 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Sky Suh
+# Date: 28 March 2024
+# Contact: sky.suh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
+# Pre-requisites: Need to have manually downloaded the data
 # Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
 #### Clean data ####
 raw_data <- read_csv("inputs/data/plane_data.csv")
@@ -41,4 +42,4 @@ cleaned_data <-
   tidyr::drop_na()
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_parquet(cleaned_data, "data/data/analysis_data.csv")

### 2024-03-28 scripts/03-test_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
+# Purpose: Tests the real analysis data based on our expectation from
 # Author: Rohan Alexander [...UPDATE THIS...]
 # Date: 11 February 2023 [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
@@ -10,6 +10,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 # [...UPDATE THIS...]
 
 #### Test data ####
+analysis_data<-read_parquet

### 2024-03-28 scripts/04-model.R

@@ -4,21 +4,22 @@
 # Date: 11 February 2023 [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
+# Pre-requisites: Need cleanaed analysis dataset from 01-data-cleaning.R
 # Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/analysis_data/analysis_data.csv")
 
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
+    formula = certainity ~ length + width,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-04-03 paper/paper.qmd

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
-author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
-date: today
-date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+title: "Attractive people, Attractive jobs "
+subtitle: "Analysis of unveilling the influence of attractiveness on Employement in the United States"
+author: Sky Suh
+thanks: "Code and data are available at: https://github.com/sjp2023/beauty-standard.git"
+date: "`r Sys.time()`"
+date-format: "D MMMM YYYY"
+abstract: "This paper is explored the influence of attractiveness on Employment regarding other subjects such as charactersitics, skills that individual had but by measuring the relationships with the attraictveness of physical, educational and gender for the hiring process and employments of the success.
+Using the data from the public dataverse source based on the paper, we found that the attractiveness impacts on employments and having higher chance to be succeed in both hriing process and careers.
+This paper provides how does the attractiveness of people impact on employment and the importance of the hughe biased based on the attracitveness only."
 format: pdf
+toc: TRUE
 number-sections: true
@@
 library(arrow)
+library(janitor)
+library(ggplot2)
+library(knitr)
+library(dplyr)
+library(readr)
 ```
@@
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+Beauty, as the attractiveness, becomes the standard of everything in the modern society as evolving into a global conversation from body shapes, flawless skin to ideal face which influences towards individual and social-cultural perspectives.
+Theses standards are being as the measurements with ourselves and others.
+For a long time, attractiveness provides the important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting the people for the first time and may have the stereotype of what is the person like.
+Furthermore, these attractiveness of people influence individuals' educations, gender not only viewing the physical shapes.
+As a result, these types of attractiveness are creating the bias particularly in the employment.
+The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand 2023].
+Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected.
+The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle 2015].
 
-The remainder of this paper is structured as follows. @sec-data....
+This paper investigates the importance of the relationship between attractiveness people and employments for both hiring process and succeed in the United States where the land of diversity and opportunity.
+I utilized data set from 2023 U.S.
+data from "University of Toronto Dataverse of Borealis" to conduct the data and analyze the connection with attractiveness people and employments regarding gender, physical and education.
+The estimand explored from this paper is, how does the attractiveness of people impact on employment with measured for 1 and 0 of classification 1 for being yes, 0 being no with physical, educational and gender attractiveness with the employment correlations.
+
+Key variables found from this analysis are 2023 data of the employment rates with the physical, educational and gender attractiveness regardless individual's skills, personalities and techniques that may support for being success in the positions in U.S., as it needs to be filled a clear gap of how does attractiveness influenced the hiring process and being employed in the organization.
+So far, we found the attractiveness will impact for the employment regarding skills, characteristics that may be the outlines for the research and how does it impacts on composite, interview and offers but with our focused area, we were interested attractiveness and employments rate.
+The findings in this paper is highlighted deep connection with the beauty/attractiveness and employments in the U.S.
+as well as the importance points since the beauty will effect on individual's first impression and provides others' feelings and stereotype itself.
+By understanding this relations, it will help to acknowledge the wrong side of the society and may provide the solutions towards the researchers and policymakers or in general to provide the right facts of attractiveness and employments.
+
+This paper is structured into the following sections: Section 2 as Data with Data Measurement, Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness, and Section 3 as Model presenting the linear regression model to justify and predict the relationships between the attractiveness and employments; Section 4 shown Results of the analysis data of model linear regression graph and Section 5 providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
 
@@
 ```
-
-Talk way more about it.
+## Data Measurement
+## Source
+## Physical Attractiveness Dataset
+## Educational Attractiveness Dataset
+## Gender Attractiveness Dataset
 
@@
 
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-04-03 paper/paper.qmd

@@
 Using the data from the public dataverse source based on the paper, we found that the attractiveness impacts on employments and having higher chance to be succeed in both hriing process and careers.
-This paper provides how does the attractiveness of people impact on employment and the importance of the hughe biased based on the attracitveness only."
+This paper provides how does the attractiveness of people impact on employment and the importance of the hughe biased based on the only attracitveness to predict whether attriactveness still deeply connects with the careers "
 format: pdf
@@
 library(arrow)
-library(janitor)
 library(ggplot2)
-library(knitr)
-library(dplyr)
-library(readr)
+
 ```
@@
 Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected.
-The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle 2015].
+The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle 2014].
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
 ## Data Measurement
@@
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
 
@@
 
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 \newpage

### 2024-04-03 scripts/00-simulate_data.R
initial commit

@@ -14,23 +14,19 @@ library(tibble)
 simulated_data <-
   tibble(
     certainty = runif(n = 1000, min = 0, max = 11) |> floor (),
-    guessed_correct = runif(n = 1000, min = 0, max = 11) |> floor (),
+    attractiveness_employment = runif(n = 1000, min = 0, max = 11) |> floor (),
   )
 
 #### Simulate data set of relationship between educational attractiveness and employment####
 
 #### Simulate data set of relationship between gender attractiveness and employment####
 
-
-### Add tests for simulated data ###
-# Expect that guessed_correct is only ever 0 or 1.
-max(simulated_data$certainity) == 1
-min(simulated_data$certainity) == 0
-any(unique(simulated_data$certainity) == c(0:1)
+# Expect that attractiveness_employment is only ever 0 or 1.
+max(simulated_data$certainty) == 1
+min(simulated_data$certainty) == 0
 
 # Expect that certainty is only ever an integer 0 to 10, inclusive.
-max(simulated_data$certainity) == 10
-min(simulated_data$certainity) == 0
-any(unique(simulated_data$certainity) == c(0:18)
+max(simulated_data$certainty) == 10
+min(simulated_data$certainty) == 0
     
 

### 2024-04-03 scripts/01-download_data.R

@@ -11,12 +11,13 @@
 library(readr)
 library(tidyverse)
 
-# Get 
-
+#### Download the data set from source ####
+# Click the data source 
+# Download as R data 
+# Open into R Studio
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+# No need to save data
+
 
          

### 2024-04-03 scripts/02-data_cleaning.R

@@ -1,45 +1,21 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Purpose: Cleans the raw plane data recorded by each physical, educational and gender attractiveness with the emplyoments and their success of their careers.
 # Author: Sky Suh
 # Date: 28 March 2024
 # Contact: sky.suh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Need to have manually downloaded the data
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv(here::here("data/raw_data/USA_data.csv"))
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+cleaned_data <- raw_data %>%
+  select(higherstatusjob, lowerstatusjob, male, female, highlyattractive, lessattractive, higheruni, middleuni, loweruni, elite_highattractive, elite_lessattractive, noneliteselective_highattractive, nonelitelower_highattractive, noneliteselective_lowattractive, nonelitelower_lowattractive)
+ 
 
 #### Save data ####
-write_parquet(cleaned_data, "data/data/analysis_data.csv")
+write_parquet(cleaned_data, here::here("data/analysis_data/analysis_data.parquet"))

### 2024-04-03 scripts/03-test_data.R

@@ -4,14 +4,13 @@
 # Date: 28 March 2024
 # Contact: sky.suh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
 # test 1
@@ -20,4 +19,4 @@ library(arrow)
 # test 4
 # test 5
 
-analysis_data<-read_parquet
+analysis_data<-read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

### 2024-04-04 scripts/03-test_data.R
initial commit

@@ -4,19 +4,118 @@
 # Date: 28 March 2024
 # Contact: sky.suh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: 
+  # 00-simulate_data.R
+  # 01-download_data.R
+  # 02-data_cleaning.R
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
+library(dplyr)
 
-
-#### Test data ####
+#### Test cleaned data ####
 # test 1
+## check if there are  2020 rows in the cleaned_data data set 
+if (nrow(cleaned_data) == 452) {
+  print("The number of TOTAL participants in cleaned_data is 2020.")
+} else {
+  print("The number of TOTAL participants in cleaned_data is not 2020.")
+}
+
+# Male
+if (nrow(data_male) == 1010) {
+  print("The number of male participants in cleaned_data is 1010.")
+} else {
+  print("The number of male participants in cleaned_data is not 1010.")
+}
+
+# Female
+if (nrow(data_female) == 1010) {
+  print("The number of female participants in cleaned_data is 1010.")
+} else {
+  print("The number of female participants in cleaned_data is not 1010.")
+}
+
+
 # test 2
+## check that employment status and attractive scores are either 0 or 1
+cleaned_data$higherstatusjob |> min() == 0
+cleaned_data$higherstatusjob |> max() == 1
+
+cleaned_data$lowerstatusjob |> min() == 0
+cleaned_data$lowerstatusjob |> max() == 1
+
+cleaned_data$highlyattractive |> min() == 0
+cleaned_data$highlyattractive |> max() == 1
+
+cleaned_data$lessattractive |> min() == 0
+cleaned_data$lessattractive |> max() == 1
+
 # test 3
+## check if there are  2020 rows in the cleaned_data data set 
+if (nrow(cleaned_data) == 2020) {
+  print("The number of TOTAL participants in cleaned_data is 2020.")
+} else {
+  print("The number of TOTAL participants in cleaned_data is not 2020.")
+}
+
+# higherstatusjob
+if (nrow(data_higherstatusjob) == 1011) {
+  print("The number of higherstatusjob participants in cleaned_data is 1011.")
+} else {
+  print("The number of higherstatusjob participants in cleaned_data is not 1011.")
+}
+
+# lowerstatusjob
+if (nrow(data_lowerstatusjob) == 1009) {
+  print("The number of lowerstatusjob participants in cleaned_data is 1009.")
[…]

### 2024-04-04 paper/paper.qmd
Update paper.qmd

@@
 library(ggplot2)
+library(kableExtra)
+library(knitr)
 
 ```
+
+#### data parquet####
+analysis_data<-read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 
@@
 As a result, these types of attractiveness are creating the bias particularly in the employment.
-The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand 2023].
+The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand].
 Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected.
-The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle 2014].
+The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle].
 
@@
 ## Data Measurement
+This paper utilizes based on the R, as the statistical Programming language [@citeR], 
 ## Source
+This dataset collected the information by survey randomly from the United States in 202 published by University of Toronto Dataverse as the part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
+
 ## Physical Attractiveness Dataset
+The physical attractiveness .vs employment dataset, represented below in @tbl-1 is shown the relationship between each variables' physical attractiveness can corresponds with the employments as higher status jobs and lower status jobs.
+This dataset, published by [
+@USA] as filed R Data updated by 2023, collects the information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employments and how does each other influencing, particularly, the beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.
+```{r}
+#| label: tbl-1
+#| tbl-cap: The dataset containing physical attractiveness and the status of employment.
+#| echo: false
+#| warning: false
+
+head (cleaned_data, 10) |>
+  kable(
+    col.names = c("higherstatusjob", "lowerstatusjob","highlyattractive", "lessattractive"),
+  booktabs = TRUE
+  )
+
+```
+
 ## Educational Attractiveness Dataset
+The educational attractiveness dataset, showed below in @tbl-2, presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
+```{r}
+#| label: tbl-2
+#| tbl-cap: The dataset containing educational attractiveness and the status of employment.
+#| echo: false
+#| warning: false
+
+head (cleaned_data, 10) |>
+  kable(
+    col.names = c("higheruni", "middleuni","loweruni", "highlyattractive", "lessattractive"),
+  booktabs = TRUE
+  )
+
+```
 ## Gender Attractiveness Dataset
+
+```{r}
+#| label: tbl-3
+#| tbl-cap: The dataset containing gender attractiveness and the status of employment.
+#| echo: false
+#| warning: false
+
+head (cleaned_data, 10) |>
+  kable(
+    col.names = c("male", "female", "highlyattractive", "lessattractive"),
+  booktabs = TRUE
+  )
+
+```
 

### 2024-04-04 paper/paper.qmd
Update paper.qmd

@@
 title: "Attractive people, Attractive jobs "
-subtitle: "Analysis of unveilling the influence of attractiveness on Employement in the United States"
+subtitle: "Analysis of unveiling the influence of attractiveness on Employement in the United States"
 author: Sky Suh
@@
 date-format: "D MMMM YYYY"
-abstract: "This paper is explored the influence of attractiveness on Employment regarding other subjects such as charactersitics, skills that individual had but by measuring the relationships with the attraictveness of physical, educational and gender for the hiring process and employments of the success.
-Using the data from the public dataverse source based on the paper, we found that the attractiveness impacts on employments and having higher chance to be succeed in both hriing process and careers.
-This paper provides how does the attractiveness of people impact on employment and the importance of the hughe biased based on the only attracitveness to predict whether attriactveness still deeply connects with the careers "
+abstract: "This paper explores the influence of attractiveness on Employment regarding other subjects such as characteristics, and skills that individuals had but by measuring the relationships with the attractiveness of physical, educational and gender for the hiring process and employment of the success.
+Using the data from the public dataverse source based on the paper, we found that attractiveness may effect employment and have a higher chance to be succeed in both hiring process and careers.
+This paper provides how does the attractiveness of people impact on employment and the importance of the huge biased based on only attractiveness to predict whether attractiveness still deeply connects with the careers "
 format: pdf
@@
 
-Beauty, as the attractiveness, becomes the standard of everything in the modern society as evolving into a global conversation from body shapes, flawless skin to ideal face which influences towards individual and social-cultural perspectives.
-Theses standards are being as the measurements with ourselves and others.
-For a long time, attractiveness provides the important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting the people for the first time and may have the stereotype of what is the person like.
-Furthermore, these attractiveness of people influence individuals' educations, gender not only viewing the physical shapes.
-As a result, these types of attractiveness are creating the bias particularly in the employment.
-The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand].
-Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected.
-The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle].
+Beauty, as attractiveness, becomes the standard of everything in modern society as evolving into a global conversation from body shapes, and flawless skin to ideal face which influences towards individual and social-cultural perspectives.
+These standards are being as the measurements of ourselves and others.
+For a long time, attractiveness has provided important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting people for the first time and may have the stereotype of what is the person like.
+Furthermore, the attractiveness of people influences individuals' education, and gender not only viewing physical shapes.
+As a result, these types of attractiveness are creating bias, particularly in employment.
+The attractive workers earn 10 to 15 percent more than average or low-looking groups [@Chand].
+Even in the diverse environmental workforce of the United States, the interplay between personal attractiveness and professional success is deeply connected.
+The way of attractiveness could shape and lead to the outcome of employment has been created by society and raised interest among scholars, researchers, and the general regarding the impact of those connections [@Ruffle].
 
-This paper investigates the importance of the relationship between attractiveness people and employments for both hiring process and succeed in the United States where the land of diversity and opportunity.
-I utilized data set from 2023 U.S.
-data from "University of Toronto Dataverse of Borealis" to conduct the data and analyze the connection with attractiveness people and employments regarding gender, physical and education.
-The estimand explored from this paper is, how does the attractiveness of people impact on employment with measured for 1 and 0 of classification 1 for being yes, 0 being no with physical, educational and gender attractiveness with the employment correlations.
+This paper investigates the importance of the relationship between attractive people and employment for both the hiring process and success in the United States where the land of diversity and opportunity.
+I utilized a data set from 2023 U.S.
+data from "The University of Toronto Dataverse of Borealis" to conduct the data and analyze the connection between the attractiveness of people and employment regarding gender, physical and education.
+The estimand explored from this paper is, how does people's attractiveness impacts employment with measured for 1 and 0 of classification 1 for being yes, 0 being no with physical, educational and gender attractiveness with the employment correlations.
 
-Key variables found from this analysis are 2023 data of the employment rates with the physical, educational and gender attractiveness regardless individual's skills, personalities and techniques that may support for being success in the positions in U.S., as it needs to be filled a clear gap of how does attractiveness influenced the hiring process and being employed in the organization.
-So far, we found the attractiveness will impact for the employment regarding skills, characteristics that may be the outlines for the research and how does it impacts on composite, interview and offers but with our focused area, we were interested attractiveness and employments rate.
-The findings in this paper is highlighted deep connection with the beauty/attractiveness and employments in the U.S.
-as well as the importance points since the beauty will effect on individual's first impression and provides others' feelings and stereotype itself.
-By understanding this relations, it will help to acknowledge the wrong side of the society and may provide the solutions towards the researchers and policymakers or in general to provide the right facts of attractiveness and employments.
+Key variables found from this analysis are 2023 data of the employment rates with the physical, educational and gender attractiveness regardless of individual's skills, personalities and techniques that may support for being a success in the positions in the U.S., as it needs to be filled a clear gap of how does attractiveness influence the hiring process and being employed in the organization.
+So far, we found the attractiveness will effect the employment regarding skills, and characteristics that may be the outlines for the research and how it impacts on composite, interview and offers but with our focused area, we were interested in attractiveness and employment rate.
+The findings in this paper highlight a deep connection between beauty/attractiveness and employment in the U.S.
+as well as the importance points since beauty will affect an individual's first impression and provides others' feelings and stereotypes itself.
+By understanding this relation, it will help to acknowledge the wrong side of society and may provide solutions towards the researchers and policymakers or in general to provide the right facts of attractiveness and employment.
 
@@
 ## Source
-This dataset collected the information by survey randomly from the United States in 202 published by University of Toronto Dataverse as the part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
+This dataset was collected the information by survey randomly from the United States in 202 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
 
 ## Physical Attractiveness Dataset
-The physical attractiveness .vs employment dataset, represented below in @tbl-1 is shown the relationship between each variables' physical attractiveness can corresponds with the employments as higher status jobs and lower status jobs.
+The physical attractiveness .vs employment dataset, represented below in @tbl-1 is shown the relationship between each variable's physical attractiveness can correspond with the employments as higher status jobs and lower status jobs.
 This dataset, published by [
-@USA] as filed R Data updated by 2023, collects the information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employments and how does each other influencing, particularly, the beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.
+@USA] as filed R Data updated by 2023, collects information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employment and how does each other influences, particularly, beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.
 ```{r}

### 2024-04-04 paper/paper.qmd
Update paper.qmd

@@
 ## Source
-This dataset was collected the information by survey randomly from the United States in 202 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
+This dataset was collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
 

### 2024-04-16 paper/paper.qmd
Update paper.qmd

@@
 
-# Model
+```{r}
+#| message: false
+#| echo: false
+#| label: fig-physical
+#| fig-cap: Physical attractives .vs employment (2023)
+cleaned_data <- select(cleaned_data)
+
+cleaned_data %>%
+  ggplot(mapping = aes(x = highlyattractive, y = higherstatusjob)) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Highly Attractive vs. Higher Status Job in 2023",
+    x = "Highly Attractive",
+    y = "Employment"
+  ) +
+  scale_fill_manual(values = c("blue", "red")) +
+  theme_classic()
 

### 2024-04-16 paper/paper.qmd
Update paper.qmd

@@
 title: "Attractive people, Attractive jobs "
-subtitle: "Analysis of unveiling the influence of attractiveness on Employement in the United States"
+subtitle: "The influence of attractiveness on Employement in the United States (2023)"
 author: Sky Suh
 thanks: "Code and data are available at: https://github.com/sjp2023/beauty-standard.git"
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
-abstract: "This paper explores the influence of attractiveness on Employment regarding other subjects such as characteristics, and skills that individuals had but by measuring the relationships with the attractiveness of physical, educational and gender for the hiring process and employment of the success.
+date: today
+date-format: long
+abstract: "This paper explores the influence of attractiveness on employment regarding other subjects such as characteristics, and skills that individuals had but by measuring the relationships with the attractiveness of physical, educational and gender for the hiring process and employment of the success.
 Using the data from the public dataverse source based on the paper, we found that attractiveness may effect employment and have a higher chance to be succeed in both hiring process and careers.
-This paper provides how does the attractiveness of people impact on employment and the importance of the huge biased based on only attractiveness to predict whether attractiveness still deeply connects with the careers "
+This paper provides how does the attractiveness of people impact on employment and the importance of the huge biased based on only attractiveness to predict whether attractiveness still deeply connects with the careers"
 format: pdf
@@
 
+cleaned_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 ```
-
-#### data parquet####
-analysis_data<-read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 
@@
 
-This paper investigates the importance of the relationship between attractive people and employment for both the hiring process and success in the United States where the land of diversity and opportunity.
+This research paper investigates the importance of the relationship between attractive people and employment for both the hiring process and success in the United States where the land of diversity and opportunity.
 I utilized a data set from 2023 U.S.
@@
 
-This paper is structured into the following sections: Section 2 as Data with Data Measurement, Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness, and Section 3 as Model presenting the linear regression model to justify and predict the relationships between the attractiveness and employments; Section 4 shown Results of the analysis data of model linear regression graph and Section 5 providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
+This paper is structured into the following sections: Section 2 as Data with Data Measurement, Data Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness as presenting as table for simple and easy view of the data, and Section 3 shown as Results of the analysis data of dataset graph based on section 2 table dataset and Section 4 providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
 
@@
 
+In this paper, Section 2.1 will be mentioned the data measurement used creating this paper and Section 2.2 will provide the resources to gather the data and information that we used to create the table sets and graphs for the results.
+Also, there will be three other sections of datasets are used; the first dataset, Section 2.3 containing the dataset of physical attractiveness and employment in 2023 in the United States.
+Following section which is 2.4 shown educational attractiveness dataset as the second data.
+The last dataset, Section 2.5, presents the relationship between employment and gender attractiveness.
+
 ## Data Measurement
-This paper utilizes based on the R, as the statistical Programming language [@citeR], 
-## Source
-This dataset was collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.
+
+This paper utilizes based on the R, as the statistical Programming language [@citeR] along with the tidyverse [@tidyverse], palmerpenguins [@palmerpenguins], arrow [@arrow], ggplot2 [@ggplot2], kableExtra [@kableExtra], readr [@readr] and knitr [@knitr] packages for generating the figures, tables and read the data for this papaer.
+
+## Data Source
+
+This dataset was extracted and collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" by Christopher Marquis, Andras Tilcsik and Ying Zhang in 2023 for gathering the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments [@USA].
 
 ## Physical Attractiveness Dataset
-The physical attractiveness .vs employment dataset, represented below in @tbl-1 is shown the relationship between each variable's physical attractiveness can correspond with the employments as higher status jobs and lower status jobs.
+The physical attractiveness .vs employment dataset, represented below in @tbl-physcial is shown the relationship between each variable's physical attractiveness can correspond with the employments as higher status jobs and lower status jobs.
 This dataset, published by [
 @USA] as filed R Data updated by 2023, collects information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employment and how does each other influences, particularly, beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.
+
 ```{r}
-#| label: tbl-1
+#| label: tbl-physcial 
 #| tbl-cap: The dataset containing physical attractiveness and the status of employment.
@@
 
-head (cleaned_data, 10) |>
+set.seed(112)
+
+cleaned_data |>
+  select(higherstatusjob, lowerstatusjob, highlyattractive, lessattractive) |>
+  slice_sample(n = 10) |>
   kable(
@@
 ## Educational Attractiveness Dataset
-The educational attractiveness dataset, showed below in @tbl-2, presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
+The educational attractiveness dataset, showed below in @tbl-education, presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
+
 ```{r}
-#| label: tbl-2
+#| label: tbl-education
 #| tbl-cap: The dataset containing educational attractiveness and the status of employment.
@@
 
-head (cleaned_data, 10) |>
+cleaned_data |>
+  slice_sample(n = 10) |>
+  select(higheruni, middleuni,loweruni, highlyattractive, lessattractive) |>
   kable(
@@
 ```{r}
-#| label: tbl-3
+#| label: tbl-gender
 #| tbl-cap: The dataset containing gender attractiveness and the status of employment.
@@
 
-head (cleaned_data, 10) |>
+cleaned_data|>
+  slice_sample(n = 10) |>
+  select(male, female, highlyattractive, lessattractive) |> 
   kable(
@@
 ```
+
+#Results
 
@@
   theme_classic()
+
+```
 

### 2024-04-20 paper/paper.qmd
Update paper.qmd

@@
 library(knitr)
+library(dplyr)
 
@@
 
-set.seed(112)
+library(kableExtra)
 
 cleaned_data |>
+  slice_sample(n = 10) |>
   select(higherstatusjob, lowerstatusjob, highlyattractive, lessattractive) |>
-  slice_sample(n = 10) |>
   kable(
@@
   )
-
 ```
@@
 
+library(kableExtra)
+
 cleaned_data |>
@@
 ```
+
 ## Gender Attractiveness Dataset
@@
 
-cleaned_data|>
+cleaned_data |>
   slice_sample(n = 10) |>
@@
   )
+slice
 
@@
 #| fig-cap: Physical attractives .vs employment (2023)
-cleaned_data <- select(cleaned_data)
+library(ggplot2)
 
-cleaned_data %>%
-  ggplot(mapping = aes(x = highlyattractive, y = higherstatusjob)) +
-  geom_bar(stat = "identity") +
+# Assuming 'cleaned_data' is your dataset
+# You might need to adjust this code according to the structure of your dataset
+
+# Select 100 random observations from the dataset
+sampled_data <- cleaned_data[sample(nrow(cleaned_data), 100), ]
+
+# Plot the bar graph
+ggplot(sampled_data, aes(x = factor(highlyattractive), fill = factor(lowerstatusjob), y = 1)) +
+  geom_bar(position = "stack", stat = "identity", color = "black") +
+  facet_wrap(~ lessattractive, nrow = 1) +
+  scale_fill_manual(values = c("blue", "red"), name = "Employment Status", labels = c("Higher Status Job", "Lower Status Job")) +
   labs(
-    title = "Highly Attractive vs. Higher Status Job in 2023",
-    x = "Highly Attractive",
-    y = "Employment"
+    title = "Correlation between Attractiveness and Employment Status",
+    x = "Attractiveness",
+    y = "Count"
   ) +
-  scale_fill_manual(values = c("blue", "red")) +
-  theme_classic()
+  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
 
+```
+
+```{r}
+sampled_data <- cleaned_data[sample(nrow(cleaned_data), 100), ]
+
+convert_to_text <- function(x) {
+  ifelse(x == 0, "less attractive", "attractive")
+}
+
+data <- data %>%
+  mutate(across(where(~all(. %in% c(0, 1))), convert_to_text))
+
+print(data)
 ```

### 2024-04-21 paper/paper.qmd
Update paper.qmd

@@
 date-format: long
-abstract: "This paper explores the influence of attractiveness on employment regarding other subjects such as characteristics, and skills that individuals had but by measuring the relationships with the attractiveness of physical, educational and gender for the hiring process and employment of the success.
-Using the data from the public dataverse source based on the paper, we found that attractiveness may effect employment and have a higher chance to be succeed in both hiring process and careers.
-This paper provides how does the attractiveness of people impact on employment and the importance of the huge biased based on only attractiveness to predict whether attractiveness still deeply connects with the careers"
+abstract: "This paper explores  the intricate dynamics between attractiveness and employment, examining how various factors such as individual characteristics, skills, and demographics intersect with physical appearance to influence the hiring process and subsequent career success.
+Leveraging data sourced from a public dataverse, our study reveals compelling insights into the role of attractiveness in shaping employment outcomes.
+Our findings suggest that attractiveness can significantly impact both the hiring process and long-term career trajectories, underscoring its relevance in contemporary employment landscapes.
+Furthermore, this paper underscores the importance of considering a broader spectrum of factors beyond attractiveness alone when predicting employment outcomes, shedding light on the pervasive biases that may arise from overly simplistic assessments."
 format: pdf
@@
 
-This paper is structured into the following sections: Section 2 as Data with Data Measurement, Data Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness as presenting as table for simple and easy view of the data, and Section 3 shown as Results of the analysis data of dataset graph based on section 2 table dataset and Section 4 providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
+This paper is structured into the following sections: @sec-data as Data with Data Measurement, Data Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness as presenting as table for simple and easy view of the data, and @sec-results shown as Results of the analysis data of dataset graph based on @sec-data table dataset and @sec-discussion providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
 
@@
 
-In this paper, Section 2.1 will be mentioned the data measurement used creating this paper and Section 2.2 will provide the resources to gather the data and information that we used to create the table sets and graphs for the results.
-Also, there will be three other sections of datasets are used; the first dataset, Section 2.3 containing the dataset of physical attractiveness and employment in 2023 in the United States.
-Following section which is 2.4 shown educational attractiveness dataset as the second data.
-The last dataset, Section 2.5, presents the relationship between employment and gender attractiveness.
+In this paper, @sec-measure will be mentioned the data measurement used creating this paper and @sec-source will provide the resources to gather the data and information that we used to create the table sets and graphs for the results.
+Also, there will be three other sections of datasets are used; the first dataset, @sec-physical containing the dataset of physical attractiveness and employment in 2023 in the United States.
+Following section which is @sec-education shown educational attractiveness dataset as the second data.
+The last dataset, @sec-gender, presents the relationship between employment and gender attractiveness.
 
-## Data Measurement
+## Data Measurement {#sec-measure}
 
@@
 
-## Data Source
+## Data Source {#sec-source}
 
-This dataset was extracted and collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" by Christopher Marquis, Andras Tilcsik and Ying Zhang in 2023 for gathering the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments [@USA].
+This dataset, published from University of Toronto Dataverse [@USA] was extracted and collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" by Christopher Marquis, Andras Tilcsik and Ying Zhang in 2023 for gathering the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments with recruited 2,500 participants had hiring experiences with bachelor's degree or higher educations, with the surveys and in total, 2,020 responses as the final samples, reached up after excluded some conditions including not completed surveys, failed to verified captcha questions and finished the survey in less than a minutes [@USA].
+In each datasets, 0 and 1 are indicated as no and yes what these meanings are the data sets, the variables are shown as 0 and 1 for each categories' sections:
+  - 0: not indicated as no for column that belongs to the specific categories 
+  - 1: indicated as yes for column that belongs to the specific categories
 
-## Physical Attractiveness Dataset
-The physical attractiveness .vs employment dataset, represented below in @tbl-physcial is shown the relationship between each variable's physical attractiveness can correspond with the employments as higher status jobs and lower status jobs.
-This dataset, published by [
-@USA] as filed R Data updated by 2023, collects information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employment and how does each other influences, particularly, beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.
+## Physical Attractiveness Dataset {#sec-physical}
+
+The dataset, referred to as Table 1 (@tbl-physcial), explores the relationship between physical attractiveness and employment outcomes, specifically concerning higher and lower status job positions.
+Published by the [@USA], this dataset comprises R Data updated through 2023 and draws from a comprehensive survey conducted among workers in the United States.
+Its primary objective is to elucidate the correlation between physical attractiveness and employment status, shedding light on how each factor influences the other.
+Notably, the dataset underscores the significance of physical beauty, a predominant aspect of attractiveness that often leaves a lasting impression and holds considerable sway in various social contexts, including the job market.
+
+The physical attractiveness data used in this table is designated as the photons that had included from the resumes of each participants.
+Highly physical attractiveness is modified as USA beauty standard while less physical attractiveness is used the actual image of university students to compare the attractiveness and perceived of people [@USA].
+
+The dataset below this paragraph includes the following variables:
+  - Higher Status Job: Indication as an individual holds a higher status job.
+  - Lower Status Job: Indication as an individual holds a lower status job.
+  - Highly Attractive: Indication as an individuals based on their perceived high level of physical attractiveness.
+  - Less Attractive: Indication as an individuals based on their perceived lower level of physical attractiveness.
 
@@
 ```
+This dataset serves as a foundational resource for examining the intricate connection between physical attractiveness and employment outcomes.
+By delving into the complexities of modern job markets, it offers valuable insights into how attractiveness influences individuals, particularly within the context of hiring processes and HR team decision-making.
+For example, participant 1 who had highly attractiveness has higher status job while less attractiveness has lower status job like respondent 10 Table 1 (@tbl-physical).
+Through rigorous analysis, this dataset illuminates the nuanced dynamics at play, providing valuable guidance for stakeholders navigating the complexities of contemporary employment landscapes.
 
-## Educational Attractiveness Dataset
-The educational attractiveness dataset, showed below in @tbl-education, presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
+## Educational Attractiveness Dataset {#sec-education}
+
+The educational attractiveness dataset, showed below in Table 2 (@tbl-education), presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
 
@@
 
-## Gender Attractiveness Dataset
+## Gender Attractiveness Dataset {#sec-gender}
 
@@
 
-#Results
+#Results {#sec-results}
 
+physical 
 ```{r}
@@
 #| label: fig-physical
-#| fig-cap: Physical attractives .vs employment (2023)
+#| fig-cap: Physical attractives .vs Employment (2023)
 library(ggplot2)
@@
   labs(
-    title = "Correlation between Attractiveness and Employment Status",
+    title = "Physical Attractiveness and Employment Status",
     x = "Attractiveness",
@@
 
+education 
 ```{r}
+#| message: false
+#| echo: false
+#| label: fig-education
+#| fig-cap: Education attractives .vs Employment (2023)
+library(ggplot2)
+library(dplyr)
+
+# Define factor levels for higheruni, middleuni, and loweruni
+sampled_data <- sampled_data %>%
+  mutate(higheruni = recode(higheruni, "0" = "Higher University", "1" = "Middle University", "2" = "Lower University"))
+
+# Plot the bar graph
+ggplot(sampled_data, aes(x = factor(higheruni), fill = factor(lowerstatusjob), y = 1)) +
+  geom_bar(position = "stack", stat = "identity", color = "black") +
+  facet_wrap(~ loweruni, nrow = 1) +
+  scale_fill_manual(values = c("blue", "red"), name = "Employment Status", labels = c("Higher Status Job", "Lower Status Job")) +
+  labs(
+    title = "Educational Attractiveness and Employment Status",
+    y = "Count"
+  ) +
+  scale_x_discrete(labels = c("Higher University", "Middle University", "Lower University")) +  # Manually setting x-axis labels
+  theme(axis.title.x=element_blank(),axis.text.x=element_text(size=12),axis.ticks.x=element_blank()) 
+```
+
+gender 
+```{r}
+#| message: false
+#| echo: false
+#| label: fig-gender
+#| fig-cap: Gender attractives .vs Employment (2023)
+
+# Select 100 random observations from the dataset
 sampled_data <- cleaned_data[sample(nrow(cleaned_data), 100), ]
 
-convert_to_text <- function(x) {
-  ifelse(x == 0, "less attractive", "attractive")
-}
+# Plot the bar graph
+ggplot(sampled_data, aes(x = factor(male), fill = factor(lowerstatusjob), y = 1)) +
+  geom_bar(position = "stack", stat = "identity", color = "black") +
+  facet_wrap(~ female, nrow = 1) +
+  scale_fill_manual(values = c("blue", "red"), name = "Employment Status", labels = c("Higher Status Job", "Lower Status Job")) +
+  labs(
+    title = "Physical Attractiveness and Employment Status",
+    x = "Attractiveness",
+    y = "Count"
+  ) +
+  scale_x_discrete(labels = c("Male", "Female")) +  # Manually setting x-axis labels
+  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 12), axis.ticks.x = element_blank())
 
-data <- data %>%
-  mutate(across(where(~all(. %in% c(0, 1))), convert_to_text))
-
-print(data)
 ```
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-04-22 paper/paper.qmd
Update paper.qmd

@@
 These standards are being as the measurements of ourselves and others.
-For a long time, attractiveness has provided important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting people for the first time and may have the stereotype of what is the person like.
+For a long time, attractiveness has provided important aspects of human interaction.
+It shapes the judgement about people as impacting on first impression when meeting people for the first time and may have the stereotype of what is the person like.
 Furthermore, the attractiveness of people influences individuals' education, and gender not only viewing physical shapes.
@@
 Even in the diverse environmental workforce of the United States, the interplay between personal attractiveness and professional success is deeply connected.
-The way of attractiveness could shape and lead to the outcome of employment has been created by society and raised interest among scholars, researchers, and the general regarding the impact of those connections [@Ruffle].
+The way attractiveness could shape and lead to the outcome of employment has been created by society and raised interest among scholars, researchers, and the general regarding the impact of those connections [@Ruffle].
 
@@
 data from "The University of Toronto Dataverse of Borealis" to conduct the data and analyze the connection between the attractiveness of people and employment regarding gender, physical and education.
-The estimand explored from this paper is, how does people's attractiveness impacts employment with measured for 1 and 0 of classification 1 for being yes, 0 being no with physical, educational and gender attractiveness with the employment correlations.
+The estimand explored from this paper is, how people's attractiveness impacts employment with measured for 1 and 0 of classification 1 being yes, 0 being no with physical, educational and gender attractiveness with the employment correlations.
 
 Key variables found from this analysis are 2023 data of the employment rates with the physical, educational and gender attractiveness regardless of individual's skills, personalities and techniques that may support for being a success in the positions in the U.S., as it needs to be filled a clear gap of how does attractiveness influence the hiring process and being employed in the organization.
-So far, we found the attractiveness will effect the employment regarding skills, and characteristics that may be the outlines for the research and how it impacts on composite, interview and offers but with our focused area, we were interested in attractiveness and employment rate.
+So far, we found that attractiveness will affect the employment regarding skills, and characteristics that may be the outlines for the research and how it impacts on composite, interview and offers but with our focused area, we were interested in attractiveness and employment rate.
 The findings in this paper highlight a deep connection between beauty/attractiveness and employment in the U.S.
-as well as the importance points since beauty will affect an individual's first impression and provides others' feelings and stereotypes itself.
-By understanding this relation, it will help to acknowledge the wrong side of society and may provide solutions towards the researchers and policymakers or in general to provide the right facts of attractiveness and employment.
+as well as the important points since beauty will affect an individual's first impression and provides others' feelings and stereotypes.
+Understanding this relationship will help to acknowledge the wrong side of society and may provide solutions for the researchers and policymakers or in general to provide the right facts of attractiveness and employment.
 
-This paper is structured into the following sections: @sec-data as Data with Data Measurement, Data Source, and each data sets of Physical Attractiveness, Educational Attractiveness, Gender Attractiveness as presenting as table for simple and easy view of the data, and @sec-results shown as Results of the analysis data of dataset graph based on @sec-data table dataset and @sec-discussion providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
+This paper is structured into the following sections: @sec-data as Data with Data Measurement, Data Source, and each data set of Physical Attractiveness, Educational Attractiveness, and Gender Attractiveness as presented as table for a simple and easy view of the data, and @sec-results shown as Results of the analysis data of dataset graph based on @sec-data table dataset and @sec-discussion providing Discussion of the implications of findings from the data set and the weakness of this paper with its next and further steps for the future study about this topic.
 
@@
 
-In this paper, @sec-measure will be mentioned the data measurement used creating this paper and @sec-source will provide the resources to gather the data and information that we used to create the table sets and graphs for the results.
-Also, there will be three other sections of datasets are used; the first dataset, @sec-physical containing the dataset of physical attractiveness and employment in 2023 in the United States.
-Following section which is @sec-education shown educational attractiveness dataset as the second data.
+In this paper, @sec-measure will mention the data measurement used in creating this paper and @sec-source will provide the resources to gather the data and information that we used to create the table sets and graphs for the results.
+Also, there will be three other sections of datasets used; the first dataset, @sec-physical contains the dataset of physical attractiveness and employment in 2023 in the United States.
+The following section which is @sec-education shows the educational attractiveness dataset as the second data.
 The last dataset, @sec-gender, presents the relationship between employment and gender attractiveness.
@@
 
-This paper utilizes based on the R, as the statistical Programming language [@citeR] along with the tidyverse [@tidyverse], palmerpenguins [@palmerpenguins], arrow [@arrow], ggplot2 [@ggplot2], kableExtra [@kableExtra], readr [@readr] and knitr [@knitr] packages for generating the figures, tables and read the data for this papaer.
+This paper utilizes based on R, as the statistical Programming language [@citeR] along with the tidyverse [@tidyverse], palmerpenguins [@palmerpenguins], arrow [@arrow], ggplot2 [@ggplot2], kableExtra [@kableExtra], readr [@readr] and knitr [@knitr] packages for generating the figures, tables and read the data for this papaer.
 
@@
 
-This dataset, published from University of Toronto Dataverse [@USA] was extracted and collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" by Christopher Marquis, Andras Tilcsik and Ying Zhang in 2023 for gathering the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments with recruited 2,500 participants had hiring experiences with bachelor's degree or higher educations, with the surveys and in total, 2,020 responses as the final samples, reached up after excluded some conditions including not completed surveys, failed to verified captcha questions and finished the survey in less than a minutes [@USA].
-In each datasets, 0 and 1 are indicated as no and yes what these meanings are the data sets, the variables are shown as 0 and 1 for each categories' sections:
-  - 0: not indicated as no for column that belongs to the specific categories 
-  - 1: indicated as yes for column that belongs to the specific categories
+This dataset, published by University of Toronto Dataverse [@USA] was extracted and collected the information by survey randomly from the United States in 2023 published by the University of Toronto Dataverse as part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" by Christopher Marquis, Andras Tilcsik and Ying Zhang in 2023 for gathering the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments with recruited 2,500 participants had hiring experiences with bachelor's degree or higher educations, with the surveys and in total, 2,020 responses as the final samples, reached up after excluded some conditions including not completed surveys, failed to verified captcha questions and finished the survey in less than a minutes [@USA].
+In each dataset, 0 and 1 are indicated as no and yes these meanings are the data sets and the variables are shown as 0 and 1 for each category's sections:
+  - 0: not indicated as no for a column that belongs to the specific categories 
+  - 1: indicated as yes for a column that belongs to the specific categories
 
@@
 
-The dataset, referred to as Table 1 (@tbl-physcial), explores the relationship between physical attractiveness and employment outcomes, specifically concerning higher and lower status job positions.
-Published by the [@USA], this dataset comprises R Data updated through 2023 and draws from a comprehensive survey conducted among workers in the United States.
-Its primary objective is to elucidate the correlation between physical attractiveness and employment status, shedding light on how each factor influences the other.
+The dataset, referred to as Table 1 (@tbl-physcial), explores the relationship between physical attractiveness and employment outcomes, specifically concerning higher and lower-status job positions.
+Published by the [@USA], this dataset comprises R Data updated through 2023 and draws from a comprehensive survey conducted among undergraduate students who have experienced for hiring process in the United States.
+Its primary objective is to explain the correlation between physical attractiveness and employment status, highlighting on how each factor influences the other.
 Notably, the dataset underscores the significance of physical beauty, a predominant aspect of attractiveness that often leaves a lasting impression and holds considerable sway in various social contexts, including the job market.
 
-The physical attractiveness data used in this table is designated as the photons that had included from the resumes of each participants.
+The physical attractiveness data used in this table is designated as the photos that were included in the resumes of each participant.
 Highly physical attractiveness is modified as USA beauty standard while less physical attractiveness is used the actual image of university students to compare the attractiveness and perceived of people [@USA].
@@
 The dataset below this paragraph includes the following variables:
-  - Higher Status Job: Indication as an individual holds a higher status job.
-  - Lower Status Job: Indication as an individual holds a lower status job.
-  - Highly Attractive: Indication as an individuals based on their perceived high level of physical attractiveness.
-  - Less Attractive: Indication as an individuals based on their perceived lower level of physical attractiveness.
+  - Higher Status Job: Indication that an individual holds a higher status job.
+  - Lower Status Job: Indication that an individual holds a lower status job.
+  - Highly Attractive: Indication as an individual based on their perceived high level of physical attractiveness.
+  - Less Attractive: Indication as an individual based on their perceived lower level of physical attractiveness.
 
@@
 By delving into the complexities of modern job markets, it offers valuable insights into how attractiveness influences individuals, particularly within the context of hiring processes and HR team decision-making.
-For example, participant 1 who had highly attractiveness has higher status job while less attractiveness has lower status job like respondent 10 Table 1 (@tbl-physical).
-Through rigorous analysis, this dataset illuminates the nuanced dynamics at play, providing valuable guidance for stakeholders navigating the complexities of contemporary employment landscapes.
+For example, participant 1 who had high attractiveness had a higher status job while less attractiveness had lower status job like respondent 10 Table 1 (@tbl-physical).
+This information, through thorough analysis, sheds light on the intricate dynamics at work, giving vital insight for stakeholders navigating the difficulties of modern employment and hiring process as follows the attractiveness.
 
@@
 
-The educational attractiveness dataset, showed below in Table 2 (@tbl-education), presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally.
+Another dataset, indicated in Table 2 (@tbl-education), delves into the concept of educational attractiveness and its implications on job status as the hiring outcomes.
+In this section, we examine the relationship between educational attractiveness and job status, particularly focusing on the influence of attending an elite and non-elite university on securing higher-status job positions as mentioned in the table.
+This dataset is sourced from the experimental designed survey conducted among undergraduate students in the USA, aimed at exploring how educational background, especially, university background, impacts the perception of attractiveness in the context of hiring processes, furthermore, biased to get hired by the organization.
+
+It mentioned above, the educational attractiveness data used in this table is sourced from the educational background of the resumes of each participant.
+To present and compare the educational attractiveness and perception of people for the hiring process, the researchers distinguished IVY League or well-known universities as higher universities, middle universities as some people know and lower universities are most people do not know [@USA].
+
+The dataset below this paragraph includes the following variables:
+  - Higher University: Indication as an individual attended very well-known or top 20 universities.
+  - Middle University: Indication as an individual attended some or few-known universities.
+  - Lower University: Indication as an individual attended not-known universities. 
+  - Higher Status Job: Indication that an individual holds a higher status job.
+  - Lower Status Job: Indication that an individual holds a lower status job.
 
@@
   slice_sample(n = 10) |>
-  select(higheruni, middleuni,loweruni, highlyattractive, lessattractive) |>
+  select(higheruni, middleuni,loweruni, higherstatusjob, lowerstatusjob) |>
   kable(
-    col.names = c("higheruni", "middleuni","loweruni", "highlyattractive", "lessattractive"),
+    col.names = c("higheruni", "middleuni","loweruni", "higherstatusjob", "lowerstatusjob"),
   booktabs = TRUE
@@
 ```
+This dataset is a valuable resource for analyzing the relationship between educational attractiveness and employment outcomes during the hiring process.
+Examining modern job markets provides insights into how education affects hiring decisions and job prospects.
+For instance, most participants who attend higher universities have higher-status jobs compared with middle and lower-university participants (@tbl-educational).
+Which, individuals who attended elite universities may have a higher chance of landing higher-status job positions than those who attended non-elite institutions.
+Through this dataset analysis, this table highlights and provides valuable guidance for stakeholders who have a difficult period or feel the unfairness of the hiring process these days with education.
 
@@
 library(ggplot2)
-
-# Assuming 'cleaned_data' is your dataset
-# You might need to adjust this code according to the structure of your dataset
 

### 2024-04-22 paper/paper.qmd
Update paper.qmd

@@
 
-The dataset below this paragraph includes the following variables:
+The educational dataset below this paragraph includes the following variables:
   - Higher University: Indication as an individual attended very well-known or top 20 universities.
@@
 
+In the last section of the data, Table 3, attributed to @tbl-gender, investigates the complex inter-connection between gender attractiveness and the status of jobs, mainly in relation to higher status and lower status of jobs depending on the individual's gender since gender is sensitive but viral argument topics for the various fields, mostly on the jobs or hiring process.
+Interestingly, this argument is continuous over 100 years but still, this is the main issue for having a job or hiring a person.
+This gender dataset was extracted from the survey conducted randomly in 2023 in the various universities' in USA [@USA] and will be derived from diverse groups of university students who have gone through various recruitment processes.
+Its main goal is to reveal the relationship between attractiveness and seniority in the job and to provide valuable insight into how gender expression affects people's perceptions in the job market.
+
+The gender attractiveness dataset provides insights into the following variables:
+  - Male: Gender presentation of individuals categorized as male.
+  - Female: Gender presentation of individuals categorized as female
+  - Higher Status Job: Indication that an individual holds a higher status job.
+  - Lower Status Job: Indication that an individual holds a lower status job.
+
 ```{r}
@@
   slice_sample(n = 10) |>
-  select(male, female, highlyattractive, lessattractive) |>
+  select(male, female, higherstatusjob, lowerstatusjob) |>
   kable(
-    col.names = c("male", "female", "highlyattractive", "lessattractive"),
+    col.names = c("male", "female", "higherstatusjob", "lowerstatusjob"),
   booktabs = TRUE
   )
-slice
 
 ```
+This dataset is crucial for analyzing the connection between gender representation and job outcomes and supports conducting the graph in @sec-results to view the differences easily with the comparison of each component with insighting into how gender attractiveness affects recruitment decisions and job seekers' perceptions in the modern job market.
+As an example, in this dataset, the ratio of males who have higher-status jobs is higher than the female contribution in prominent jobs but females have more ratio in lower-status jobs.
 
@@
 
-physical 
+## Hire because of physical Attractiveness
+
+To determine the relationship between physical attractiveness and employment status per individual, a merged and summarized data set was created with variables for high attractiveness, less attractiveness and employment status (higher status job, lower status job) as shown in Table 1 (see @tbl-physical).
+Figure 1 @fig-physical, the bar graph, shows the distribution of employment status across different levels of physical attractiveness as the individual examined using a sample of 100 observations randomly from the dataset.
+Each bar represents the count of individuals categorized based on their perceived level of attractiveness, with distinctions made between those holding higher-status jobs and those in lower-status positions.
+The x-axis denotes attractiveness levels, while the y-axis represents the count of individuals.
 ```{r}
@@
 #| label: fig-physical
-#| fig-cap: Physical attractives .vs Employment (2023)
+#| fig-cap: Physical attractiveness .vs Employment (2023)
 library(ggplot2)
@@
 ```
+As presented in Figure 1 @fig-physical, what could be noted was that 21 counted of highly attractive participants have lower status jobs in the sampled data of 100 while 27 less attractive stakeholders are counted as having lower positions.
+For higher-status jobs, 27 higher attractive people have higher ranking positions, in the meantime, 25 less attractive people have lower positions.
+Upon visual, it is evident that individuals perceived to be very attractive tend to have a higher proportion of jobs in higher positions than those who are perceived to be less attractive.
+On the contrary, those who are considered unattractive are more widely spread in lower-ranking occupations.
+There might be slight differences but this is only 100 observations, in cleaned data, it has 2020 observations; what it means the differences between high and less attractive participants will be huge.
 
-education 
+## Better education, better jobs
+
 ```{r}
@@
 #| label: fig-education
-#| fig-cap: Education attractives .vs Employment (2023)
+#| fig-cap: Education attractiveness .vs Employment (2023)
 library(ggplot2)
@@
 ```
+To analyze the relationship between educational background (while attending university) and employment status, we constructed an analyzed summary dataset and marginalized variables of education attractiveness depending on the level of the university (high, middle and low), and employment status.
+This dataset is detailed in Table 2 (see @tbl-education).
+Figure 2 @fig-education, same as figure 1 @fig-physical, the bar graph, presents the implications of a better university providing a better job status in the sampled data of 100 observations that were randomly distrusted.
 
-gender 
+For Figure 2 @fig-education, as mentioned above in this paragraph, a sample of 100 observations was randomly selected from the dataset to represent the broader undergraduate/graduated students in USA.
+Each bar in the graph represents the count of individuals categorized based on their perceived level of educational attractiveness and the status of their employment (higher status job or lower status job).
+
+What @fig-education has shown above that bar graph, every 18 participants in both three universities have a higher status job but the students in the higher university have fewer counts for lower status jobs - 15, 17 participants are counted as lower ranking positions in the middle university while total 25 students attending in the lower university have very low status for their jobs.
+This analysis provides insight into how attending an elite university affects an individual's chances of securing a higher-ranking job and highlights the interaction between educational background and career outcomes.
+
+## Gender perception, employment perception
+
+To explore the relationship between gender attractiveness and employment status, a comprehensive dataset was synthesized with the variables of gender attractiveness - male and female, and job status.
+This dataset is outlined in Table 3 (see @tbl-gender).
+Figure 3, referred to as Figure @fig-gender, visually illustrates this association through a bar graph.
+Same as figure 1@fig-physical and figure 2@fig-education, a representative sample of this dataset is 100 observations drawn randomly from the experimental designed surveys in the US.
+Each bar within the graph signifies the count of individuals based on their perceived gender attractiveness and their respective employment status (higher status job or lower status job).
+
+According to Figure 3, @fig-gender found that among 100 participants, 25 females held lower-status jobs compared to 24 males, while 25 higher-status jobs were held by female participants and 26 by male stakeholders.
+Visually, it was evident that males were perceived as more attractive and had a higher likelihood of securing better jobs than females for various reasons.
+Although the gap between gender and employment status was small in this sample, it is important to note that the dataset contained 2020 observations, indicating that the differences may be significant depending on the gender of the participants.
+
 ```{r}
@@
 #| label: fig-gender
-#| fig-cap: Gender attractives .vs Employment (2023)
+#| fig-cap: Gender attractiveness .vs Employment (2023)
 
@@
   labs(
-    title = "Physical Attractiveness and Employment Status",
+    title = "Gender Attractiveness and Employment Status",
     x = "Attractiveness",
@@
 
-## First discussion point {#sec-first-point}
+As evidenced by the results, there are a few points that should be pointed out with three major objections aimed at this paper.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Highly attractive influences to get the higher status jobs during the hiring process {#sec-attract}
 
-## Second discussion point
+## Elite and well-known university improves the chance to have a better job {#sec-university}
 
-## Third discussion point
+## Males advance the improved career opportunity {#sec-sex}
 

### 2024-04-22 paper/Attractive people, Attractive jobs.qmd
Update and rename paper.qmd to Attractive people, Attractive jobs.qmd

--- 2024-04-22 paper/paper.qmd
@@
 title: "Attractive people, Attractive jobs "
-subtitle: "The influence of attractiveness on Employement in the United States (2023)"
+subtitle: "The influence of attractiveness on Employment in the United States (2023)"
 author: Sky Suh
@@
 date-format: long
-abstract: "This paper explores  the intricate dynamics between attractiveness and employment, examining how various factors such as individual characteristics, skills, and demographics intersect with physical appearance to influence the hiring process and subsequent career success.
-Leveraging data sourced from a public dataverse, our study reveals compelling insights into the role of attractiveness in shaping employment outcomes.
-Our findings suggest that attractiveness can significantly impact both the hiring process and long-term career trajectories, underscoring its relevance in contemporary employment landscapes.
-Furthermore, this paper underscores the importance of considering a broader spectrum of factors beyond attractiveness alone when predicting employment outcomes, shedding light on the pervasive biases that may arise from overly simplistic assessments."
+abstract: "This paper delves into the complex relationship between physical attractiveness and employment, exploring how various factors such as individual characteristics, skills, and demographics intersect with physical appearance to influence the hiring process and subsequent career success.
+Our study makes use of data sourced from the University of Toronto dataverse, and reveals interesting insights into the role of attractiveness in shaping employment outcomes.
+Our findings suggest that physical attractiveness can have a significant impact on both the hiring process and long-term career trajectories, highlighting its relevance in employment and hiring sessions.
+Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes, to shed light on the pervasive biases that may arise from overly simplistic assessments."
 format: pdf
@@
 
-cleaned_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+cleaned_data <- read_parquet(here::here("analysis_data.parquet"))
 ```
@@
 
-This paper utilizes based on R, as the statistical Programming language [@citeR] along with the tidyverse [@tidyverse], palmerpenguins [@palmerpenguins], arrow [@arrow], ggplot2 [@ggplot2], kableExtra [@kableExtra], readr [@readr] and knitr [@knitr] packages for generating the figures, tables and read the data for this papaer.
+This paper utilizes based on R, as the statistical Programming language [@citeR] along with the tidyverse [@tidyverse], palmerpenguins [@palmerpenguins], arrow [@arrow], ggplot2 [@ggplot2], kableExtra [@kableExtra], tbble [@tibble], readr [@readr], knitr [@knitr] and dplyr [@dplyr] packages for generating the figures, tables and read the data for this papaer.
 
@@
 
-The dataset, referred to as Table 1 (@tbl-physcial), explores the relationship between physical attractiveness and employment outcomes, specifically concerning higher and lower-status job positions.
+The dataset, referred to as Table 1 (@tbl-physical), explores the relationship between physical attractiveness and employment outcomes, specifically concerning higher and lower-status job positions.
 Published by the [@USA], this dataset comprises R Data updated through 2023 and draws from a comprehensive survey conducted among undergraduate students who have experienced for hiring process in the United States.
@@
 ```{r}
-#| label: tbl-physcial 
+#| label: tbl-physical 
 #| tbl-cap: The dataset containing physical attractiveness and the status of employment.
@@
 Examining modern job markets provides insights into how education affects hiring decisions and job prospects.
-For instance, most participants who attend higher universities have higher-status jobs compared with middle and lower-university participants (@tbl-educational).
+For instance, most participants who attend higher universities have higher-status jobs compared with middle and lower-university participants (@tbl-education).
 Which, individuals who attended elite universities may have a higher chance of landing higher-status job positions than those who attended non-elite institutions.
@@
 
-#Results {#sec-results}
+# Results {#sec-results}
 
@@
 To determine the relationship between physical attractiveness and employment status per individual, a merged and summarized data set was created with variables for high attractiveness, less attractiveness and employment status (higher status job, lower status job) as shown in Table 1 (see @tbl-physical).
-Figure 1 @fig-physical, the bar graph, shows the distribution of employment status across different levels of physical attractiveness as the individual examined using a sample of 100 observations randomly from the dataset.
+@fig-physical, the bar graph, shows the distribution of employment status across different levels of physical attractiveness as the individual examined using a sample of 100 observations randomly from the dataset.
 Each bar represents the count of individuals categorized based on their perceived level of attractiveness, with distinctions made between those holding higher-status jobs and those in lower-status positions.
@@
 ```
-As presented in Figure 1 @fig-physical, what could be noted was that 21 counted of highly attractive participants have lower status jobs in the sampled data of 100 while 27 less attractive stakeholders are counted as having lower positions.
+As presented in @fig-physical, what could be noted was that 21 counted of highly attractive participants have lower status jobs in the sampled data of 100 while 27 less attractive stakeholders are counted as having lower positions.
 For higher-status jobs, 27 higher attractive people have higher ranking positions, in the meantime, 25 less attractive people have lower positions.
@@
 This dataset is detailed in Table 2 (see @tbl-education).
-Figure 2 @fig-education, same as figure 1 @fig-physical, the bar graph, presents the implications of a better university providing a better job status in the sampled data of 100 observations that were randomly distrusted.
+@fig-education, same as @fig-physical, the bar graph, presents the implications of a better university providing a better job status in the sampled data of 100 observations that were randomly distrusted.
 
-For Figure 2 @fig-education, as mentioned above in this paragraph, a sample of 100 observations was randomly selected from the dataset to represent the broader undergraduate/graduated students in USA.
+For @fig-education, as mentioned above in this paragraph, a sample of 100 observations was randomly selected from the dataset to represent the broader undergraduate/graduated students in USA.
 Each bar in the graph represents the count of individuals categorized based on their perceived level of educational attractiveness and the status of their employment (higher status job or lower status job).
@@
 This dataset is outlined in Table 3 (see @tbl-gender).
-Figure 3, referred to as Figure @fig-gender, visually illustrates this association through a bar graph.
-Same as figure 1@fig-physical and figure 2@fig-education, a representative sample of this dataset is 100 observations drawn randomly from the experimental designed surveys in the US.
+Figure 3, referred to as @fig-gender, visually illustrates this association through a bar graph.
+Same as @fig-physical and @fig-education, a representative sample of this dataset is 100 observations drawn randomly from the experimental designed surveys in the US.
 Each bar within the graph signifies the count of individuals based on their perceived gender attractiveness and their respective employment status (higher status job or lower status job).
 
-According to Figure 3, @fig-gender found that among 100 participants, 25 females held lower-status jobs compared to 24 males, while 25 higher-status jobs were held by female participants and 26 by male stakeholders.
+According to @fig-gender, found that among 100 participants, 25 females held lower-status jobs compared to 24 males, while 25 higher-status jobs were held by female participants and 26 by male stakeholders.
 Visually, it was evident that males were perceived as more attractive and had a higher likelihood of securing better jobs than females for various reasons.
@@
 As evidenced by the results, there are a few points that should be pointed out with three major objections aimed at this paper.
+First point @sec-attract will mention about the result of physical attractiveness affect to the employment status; next section, @sec-university talks the educational background can influence to have a better job.
+Lastly, gender attractiveness improve and advance the career opportunity in @sec-sex.
 
@@
 
+Physical attractiveness is melted into the part of people’s life and judged by society.
+When it comes to landing a higher-status job, several highly attractive influences can make people stand out from other candidates, particularly, during the hiring process.
+Appearance plays a crucial role in forming initial impressions during interactions which will be the interview session for the employment with contributing the perceptions of the professionalism.
+According to Karen Dion, Research suggests that individuals perceived as physically attractive may benefit from implicit biases, as they are often perceived as more competent, trustworthy, and capable [@Dion].
+In which, provides the advantages to the candidates for HR managers where positive initial impressions can shape the better qualification and sustainability for the roles.
+It leads to attractive people having a higher chance to get higher-status jobs or enhance their careers and investing in physical appearance to raise the attractiveness will help to advance career prospects.
+
 ## Elite and well-known university improves the chance to have a better job {#sec-university}
+
+Another point to discuss in this paper is high-ranking and well-known universities have higher chances to get a better job.
+These days, the reputation and prestige of a university are important and it can impact on the employment status or hiring process.
+These universities are offering graduates a clear advantage in the job market.
+Employers view candidates who graduate from prestigious universities favourably, thinking they have a higher level of education, skills, and qualifications which recruiters and hiring managers are inclined to prioritize candidates who hold degrees from elite institutions due to the perceived quality of education and training they receive.
+Researchers investigate that the increasing admission and graduation rates in higher-ranking universities, allow employers to recruit better and more talented individuals [@Nogales].
+Not only the fame but also the institutions have access to extensive networks and opportunities for career advancement, As a result, employers are able to seek out future employees from the graduated students from well-known universities actively.
+On the other hand, middle or lower universities have less chance to have higher-status jobs due to the lack of networking and fame which are less attractive than high-rank schools.
 
@@
 
-## Weaknesses and next steps
+The last discussion to point out is gender, a huge impact on employment practices and career opportunities, and it is one of the most enduring, controversial, and widely studied topics in various disciplines over a century.
+The importance of gender dynamics in the employment context remains a central point of social discussion and cannot be overstated.
+The impact of gender on employment processes or career trajectories is multifaceted and complex due to the stereotypes from history which maintain gender discrimination and prejudice in employment practices, and certain industries and positions are disproportionately dominated by males specifically.
+What Kubiak wrote in the paper was gender biases' impact on hiring decisions remained an issue [@Kubiak].
+Even Figure 3 (see @fig-gender) provides the different gaps between females and males for job status and if it covers all 2020 respondents, the gaps will be hugely different.
 
-Weaknesses and next steps should also be included.
+## Weaknesses and Next steps
 
-\newpage
+### Weakness
 
-\appendix
+The limitation of using data from Dataverse at the University of Toronto is the format of the variables which are predominantly answered as binary values (0 or 1) rather than categorical responses (yes or no).
+This formatting issue poses challenges when converting the data into tables and graphs in this paper to present as data and results.
+For instance, figures @fig-education and @fig-gender, the x-axis captions cannot be effectively managed but overlapped, and the labels displaying 0 and 1 above the graphs cannot be removed.
+This limitation restricts the clarity and comprehensibility of the visual representations of the data visualized as the graphs but hindering the ability to convey meaningful insights to readers.
+Moreover, the prevalence of binary variables in the dataset causes the risk of error data interpretation.
+The presence of 0 and 1 values may lead the system to misinterpret certain variables as missing or incorrect data, potentially resulting in inaccuracies in the generated tables and graphs.
+Such inaccuracies can compromise the sample data from the dataset.
 
-# Appendix {-}
+### Next steps
+
+A possible next step could be to explore how different characteristics/interpersonal skills that each individual has with different academic backgrounds and attractiveness can influence employment status with an individual’s gender and the relationship between characteristics of individual and job status regardless of physical, gender and educational background attractiveness but what HR teams or supervisors think about each person itself without any perceptions components.
+Additionally, we could also create a model section to make a linear regression model to present the differences.
+Regarding the binary responses in the dataset, instead of 0 and 1, simple but straightforward answers (Yes and No) could be done to be beneficial and improve the overall analysis, the quality of graphs and the paper.
+Furthermore, the visualization of a separated graph model to easy to compare each component would be helpful to advance the quality of this paper.
 

### 2024-04-22 scripts/04-model.R
Delete scripts/04-model.R

@@ -1,38 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: Need cleanaed analysis dataset from 01-data-cleaning.R
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(arrow)
-
-#### Read data ####
-analysis_data <- read_parquet("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = certainity ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
-
-

### 2024-04-22 paper/Attractive_people,_Attractive_jobs.qmd
Update Attractive_people,_Attractive_jobs.qmd

--- 2024-04-22 paper/Attractive people, Attractive jobs.qmd
@@
 date-format: long
-abstract: "This paper delves into the complex relationship between physical attractiveness and employment, exploring how various factors such as individual characteristics, skills, and demographics intersect with physical appearance to influence the hiring process and subsequent career success.
-Our study makes use of data sourced from the University of Toronto dataverse, and reveals interesting insights into the role of attractiveness in shaping employment outcomes.
-Our findings suggest that physical attractiveness can have a significant impact on both the hiring process and long-term career trajectories, highlighting its relevance in employment and hiring sessions.
-Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes, to shed light on the pervasive biases that may arise from overly simplistic assessments."
+abstract: "This paper delves into the relationship between attractiveness and employment, exploring how various factors such as individual characteristics, skills, and demographics intersect with physical appearance, educational background and gender to influence the hiring process and subsequent career success.
+Our study makes use of data sourced from the University of Toronto dataverse, and reveals interesting insights into the role of attractiveness in shaping employment outcomes and the status of jobs.
+Our findings suggest that most socio-demographic attractiveness including appearance, education and sex can have a significant impact on both the hiring process and long-term career, highlighting its relevance in employment and hiring sessions.
+Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes as physical, educational background and gender with the correlation fo those variables."
 format: pdf
@@
 The dataset below this paragraph includes the following variables:
-  - Higher Status Job: Indication that an individual holds a higher status job.
-  - Lower Status Job: Indication that an individual holds a lower status job.
-  - Highly Attractive: Indication as an individual based on their perceived high level of physical attractiveness.
-  - Less Attractive: Indication as an individual based on their perceived lower level of physical attractiveness.
+
+  * Higher Status Job: Indication that an individual holds a higher status job.
+  * Lower Status Job: Indication that an individual holds a lower status job.
+  * Highly Attractive: Indication as an individual based on their perceived high level of physical attractiveness.
+  * Less Attractive: Indication as an individual based on their perceived lower level of physical attractiveness.
 
@@
 The educational dataset below this paragraph includes the following variables:
-  - Higher University: Indication as an individual attended very well-known or top 20 universities.
-  - Middle University: Indication as an individual attended some or few-known universities.
-  - Lower University: Indication as an individual attended not-known universities. 
-  - Higher Status Job: Indication that an individual holds a higher status job.
-  - Lower Status Job: Indication that an individual holds a lower status job.
+
+  * Higher University: Indication as an individual attended very well-known or top 20 universities.
+  * Middle University: Indication as an individual attended some or few-known universities.
+  * Lower University: Indication as an individual attended not-known universities. 
+  * Higher Status Job: Indication that an individual holds a higher status job.
+  * Lower Status Job: Indication that an individual holds a lower status job.
 
@@
 The gender attractiveness dataset provides insights into the following variables:
-  - Male: Gender presentation of individuals categorized as male.
-  - Female: Gender presentation of individuals categorized as female
-  - Higher Status Job: Indication that an individual holds a higher status job.
-  - Lower Status Job: Indication that an individual holds a lower status job.
+
+  * Male: Gender presentation of individuals categorized as male.
+  * Female: Gender presentation of individuals categorized as female
+  * Higher Status Job: Indication that an individual holds a higher status job.
+  * Lower Status Job: Indication that an individual holds a lower status job.
 
@@
   labs(
-    title = "Physical Attractiveness and Employment Status",
     x = "Attractiveness",
@@
   labs(
-    title = "Educational Attractiveness and Employment Status",
     y = "Count"
@@
   labs(
-    title = "Gender Attractiveness and Employment Status",
     x = "Attractiveness",

### 2024-04-22 paper/Attractive_people,_Attractive_jobs.qmd
Update Attractive_people,_Attractive_jobs.qmd

@@
 Our findings suggest that most socio-demographic attractiveness including appearance, education and sex can have a significant impact on both the hiring process and long-term career, highlighting its relevance in employment and hiring sessions.
-Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes as physical, educational background and gender with the correlation fo those variables."
+Additionally, this paper emphasizes the importance of considering a broader range of factors beyond attractiveness alone when predicting employment outcomes as physical, educational background and gender with the correlation of those variables."
 format: pdf
